# Ebullition Analysis

I want to evaluate the relationship between ebullitive flux of CH4 and depth and distance to the inlet. I hypothesized that both depth and distance to the inlet will be negatively associated with ebullitive flux. Ultimately, we have to deal with the fact that the data are zero-inflated and bounded by 0. I tried multiple models below to address these characteristics
```{r eb analysis set up}
eb_all <- bind_rows(sister3_pts_22_eb %>% mutate(Site ="Sister3"), 
                    pick_pts_13_eb,
                    catfish_pts_18_eb %>% dplyr::select(-c(catfish_dist_1, catfish_dist_2)),
                    catfish_pts_06_eb %>% dplyr::select(-c(catfish_dist_1, catfish_dist_2)),
                    deans_pts_30_eb %>% dplyr::select(-c(deans_dist_1, deans_dist_2)),
                    deans_pts_16_eb%>% dplyr::select(-c(deans_dist_1, deans_dist_2))) %>% 
  mutate(Site = as.factor(Site))%>% 
  mutate(Depth_scale = scale(Depth), inlet_dist_scale = scale(inlet_dist))

ebullition_24 <- eb_all %>% 
  mutate(ch4_eb_g = gas_vol_corrected * (1/10^6) * ch4_conc * (1/10^3) * 16.04 * (1/0.0821)* (1/293.15), 
         Collection.Start.Date = case_when(
           Sampling == "Deans1" ~ ymd("2022-08-16"),
           Sampling == "Deans2" ~ ymd("2022-08-30"), 
           Sampling == "Catfish1" ~ ymd("2022-09-06"),
           Sampling == "Catfish2" ~ ymd("2022-09-18"), 
           Sampling == "Pick1" ~ ymd("2022-09-13"),
           Sampling == "Sister31" ~ ymd("2022-08-22")
         )) %>% 
  mutate(time_hr_na = if_else(is.na(ch4_eb_g), NA_real_, time_hr)) %>% 
  group_by(Site, Trap, Sampling, Collection.Start.Date, inlet_dist, Depth, inlet_dist_scale, Depth_scale) %>% 
  summarize(sum_time = sum(time_hr_na, na.rm = T), sum_g = sum(ch4_eb_g, na.rm = T)) %>% 
  mutate(area = pi * 81 * 0.0001, ch4_eb_g_m2_hr_24 = sum_g * (1/area)* (1/sum_time))
```

## Plots
```{r dist and depth plot, echo = F}
# Depth and inlet distance are correlated, VIF of mod1 = 1.2
cor.test(eb_all$Depth, eb_all$inlet_dist, method = "spearman")

ggplot(eb_all, aes(Depth, ch4_eb_g_m2_hr, color = Site)) + geom_point()
ggplot(eb_all, aes(inlet_dist, ch4_eb_g_m2_hr, color = Site)) + geom_point()

```

## Mod1: Non-zero data, fixed effects only
```{r fixed non zero, echo =F}
# no random effects and no zeros because gamma can't handle zeros
mod1 <- glm(ch4_eb_g_m2_hr ~ Depth_scale + inlet_dist_scale, data = eb_all %>% filter(ch4_eb_g_m2_hr > 0), family = Gamma(link = "log"))
summary(mod1)
```

## Mod2: Non zero data, mixed model
```{r mixed non zero, echo = F}
# with random effects but still no zeros
mod2 <- glmer(ch4_eb_g_m2_hr ~ Depth_scale + inlet_dist_scale + (1|Sampling)  + (1|trip_wr), data = eb_all %>% filter(ch4_eb_g_m2_hr > 0), family = Gamma(link = "log"))
summary(mod2)

sd(eb_all %>% filter(ch4_eb_g_m2_hr>0) %>% pull(Depth), na.rm=T)
sd(eb_all %>% filter(ch4_eb_g_m2_hr>0) %>% pull(inlet_dist), na.rm=T)
```

## Mod2.a: Non zero data, mixed model without Picks
```{r no pick mixed non zero, echo = F}
mod2.a <- glmer(ch4_eb_g_m2_hr ~ Depth_scale + inlet_dist_scale + (1|Sampling)  + (1|trip_wr), data = eb_all %>% filter(ch4_eb_g_m2_hr > 0, Site != "Picks"), family = Gamma(link = "log"))
summary(mod2.a)

sd(eb_all %>% filter(ch4_eb_g_m2_hr>0, Site != "Picks") %>% pull(Depth), na.rm=T)
sd(eb_all %>% filter(ch4_eb_g_m2_hr>0, Site != "Picks") %>% pull(inlet_dist), na.rm=T)
```

## Mod2.b: Non zero data, mixed model only Picks
```{r pick mixed non zero, echo = F}
mod2.b <- glmer(ch4_eb_g_m2_hr ~ Depth_scale + inlet_dist_scale + (1|trip_wr), data = eb_all %>% filter(ch4_eb_g_m2_hr > 0, Site == "Picks"), family = Gamma(link = "log"))
summary(mod2.b)
```

## Mod3: Logistic regression, fixed effects only
```{r logistic fixed, echo = F}
mod3 <- glm(ch4_eb_bin ~ Depth_scale + inlet_dist_scale, data = eb_all %>% mutate(ch4_eb_bin = if_else(ch4_eb_g_m2_hr>0, 1,0)), family = binomial(link = "logit"))
summary(mod3)
```

## Mod4: Logistic regression, mixed model
```{r logistic mixed, echo = F}
mod4 <- glmer(ch4_eb_bin ~ Depth_scale + inlet_dist_scale + (1|Sampling) + (1|trip_wr), data = eb_all %>% mutate(ch4_eb_bin = if_else(ch4_eb_g_m2_hr>0, 1,0)), family = binomial(link = "logit"))
summary(mod4)
```

## Mod4.a: Logistic regression, mixed model without Picks
```{r no pick logistic mixed, echo = F}
mod4.a <- glmer(ch4_eb_bin ~ Depth_scale + inlet_dist_scale + (1|Sampling) + (1|trip_wr), data = eb_all %>% filter(Site != "Picks") %>% mutate(ch4_eb_bin = if_else(ch4_eb_g_m2_hr>0, 1,0)), family = binomial(link = "logit"))
summary(mod4.a)
```

## Mod4.b: Logistic regression, mixed model only Picks
```{r pick logistic, echo = F}
mod4.b <- glm(ch4_eb_bin ~ Depth_scale + inlet_dist_scale, data = eb_all %>% filter(Site == "Picks") %>% mutate(ch4_eb_bin = if_else(ch4_eb_g_m2_hr>0, 1,0)), family = binomial(link = "logit"))
summary(mod4.b)
```

## Mod5: Hurdle model, predictors generate structural zeros
```{r hurdle pred, echo = F}
mod5 <- glmmTMB(ch4_eb_g_m2_hr ~ Depth_scale + inlet_dist_scale + (1|Sampling)  + (1|trip_wr), data = eb_all %>% filter(is.na(ch4_eb_g_m2_hr)==F) %>% st_drop_geometry(),  ziformula = ~., family = ziGamma)
summary(mod5)
```

## Model selection with Mod5 predictors
```{r model selection hurdle, echo = F}
mod5.a <-  glmmTMB(ch4_eb_g_m2_hr ~ Depth_scale + (1|Sampling)  + (1|trip_wr), data = eb_all %>% filter(is.na(ch4_eb_g_m2_hr)==F) %>% st_drop_geometry(),  ziformula = ~., family = ziGamma)
mod5.b <- glmmTMB(ch4_eb_g_m2_hr ~ inlet_dist_scale + (1|Sampling)  + (1|trip_wr), data = eb_all %>% filter(is.na(ch4_eb_g_m2_hr)==F) %>% st_drop_geometry(),  ziformula = ~., family = ziGamma)

cand.models <- list("mod5"=mod5, 
                    "mod5.a"=mod5.a,
                    "mod5.b"=mod5.b)

aictab(cand.models)

summary(mod5.b)
```

## Mod6: Hurdle model, equal probability of structural zeros
```{r hurdle no pred, echo = F}
mod6 <- glmmTMB(ch4_eb_g_m2_hr ~ Depth_scale + inlet_dist_scale + (1|Sampling)  + (1|trip_wr), data = eb_all %>% filter(is.na(ch4_eb_g_m2_hr)==F) %>% st_drop_geometry(),  ziformula = ~1, family = ziGamma)
summary(mod6)
```

## Mod7: Not broken up by time, no longer zero-inflated, sampling random effect
```{r aggregated gamma, echo = F}
mod7 <- glmer(ch4_eb_g_m2_hr_24 ~ Depth + inlet_dist + (1|Sampling) , data = ebullition_24 %>% filter(ch4_eb_g_m2_hr_24 > 0), family = Gamma(link = "log"))
summary(mod7)

mod7.a <- glmer(ch4_eb_g_m2_hr_24 ~ inlet_dist + (1|Sampling) , data = ebullition_24 %>% filter(ch4_eb_g_m2_hr_24 > 0), family = Gamma(link = "log"))
mod7.b <- glmer(ch4_eb_g_m2_hr_24 ~ Depth + (1|Sampling) , data = ebullition_24 %>% filter(ch4_eb_g_m2_hr_24 > 0), family = Gamma(link = "log"))

summary(mod7.b)

cand.models <- list("mod7"=mod7, 
                    "mod7.a"=mod7.a,
                    "mod7.b"=mod7.b)

aictab(cand.models)
```

```{r plot depth gamma, echo = F}
pred.mod7.b <- ggpredict(mod7.b, terms =c("Depth", "Sampling"), type = "random") 

#png(filename = "4-Figures/eb-analysis-summary.png", width = 8, height = 5, units = "in", res = 300)
ggplot(pred.mod7.b) +
  #geom_ribbon(aes(fill = group, x = x, ymin = conf.low, ymax = conf.high), alpha = 0.5)+
 
  geom_point(data=ebullition_24, 
             aes(x=Depth, y = ch4_eb_g_m2_hr_24, color=Sampling),
             size = 2.5)+
   geom_line(aes(x=x, y=predicted, color = group))+
  scale_color_manual(values = c("#2F4A4A","#588B9B", "#A9707F","#D1A6B2", "#CEB59B", "#C7C7C7"),
                     labels = c("Catfish 09/06/22", "Catfish 09/18/22", "Deans 08/16/22", "Deans 08/30/22", "Pick 09/13/22", "Sister 08/22/22"))+
  ylab(expression(CH[4]~ flux ~ (g~m^-2~hr^-1)))+
  xlab("Depth (m)")+
  theme_bw()+
  theme(legend.title = element_blank(), axis.text = element_text(size = 14, color = "black"), axis.title = element_text(size = 16, color = "black"), legend.text = element_text(size = 14))
#dev.off()
```


