--- 
title: "Naslund Chapter 1 Analysis"
author: "Laura Naslund"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography:
- book.bib
- packages.bib
description: |
  This is a minimal example of using the bookdown package to write a book.
  set in the _output.yml file.
  The HTML output format for this example is bookdown::gitbook,
link-citations: yes
github-repo: "rstudio/bookdown-demo"
---

# Sampling scheme

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
```{r left over minimal example text, include=F}
#This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports; for example, a math equation $a^2 + b^2 = c^2$.
```

```{r about setup, include=F}
library(tidyverse)
library(mapview)
library(lubridate)
library(sf)
library(data.table)
library(dygraphs)
library(xts)

trap_locations <- read.csv("2-Clean Data/ebullition-trap-locations.csv") %>% 
  filter(str_sub(Name, 2,2) %>% str_detect("[:alpha:]")==F) %>% 
  st_as_sf(coords = c("Longitude", "Latitude"), crs=4326) %>% st_transform(crs = 32617)%>% 
  mutate(Site = case_when(
    str_sub(Name, 1, 1) == "P" ~"Pick",
    str_sub(Name, 1, 1) == "D" ~"Deans",
    str_sub(Name, 1, 1) == "S" ~"Sister3",
    str_sub(Name, 1, 1) == "C" ~"Catfish",
  )) %>% 
  select(-Description)

inlet_locations <- read.csv("2-Clean Data/inlet-locations.csv") %>% 
  st_as_sf(coords = c("Longitude", "Latitude"), crs=4326) %>% st_transform(crs = 32617)

deans <- read_sf("2-Clean Data/site_shapefiles/Deans.shp") %>% st_transform(crs = 32617)
catfish <- read_sf("2-Clean Data/site_shapefiles/Catfish.shp") %>% st_transform(crs = 32617)
sister3 <- read_sf("2-Clean Data/Site_Shapefiles/Sister3.shp") %>% st_transform(crs = 32617)
pick <- read_sf("2-Clean Data/Site_Shapefiles/Pick.shp") %>% st_transform(crs = 32617)

trap_locations %>% mutate(Site = case_when(
  str_sub(Name, 1, 1) == "P" ~"Pick",
  str_sub(Name, 1, 1) == "D" ~"Deans",
  str_sub(Name, 1, 1) == "S" ~"Sister3",
  str_sub(Name, 1, 1) == "C" ~"Catfish",
)) %>% tail()
```

```{r, include = F}

q <- read.csv("2-Clean Data/discharge.csv") %>% 
  mutate(q = ((Vol_ml*10^-6)/Time_s), 
         Vol_m3 = case_when(Site == "Deans" ~ st_area(deans) %>% as.numeric()*2.03, 
                             Site == "Catfish" ~ st_area(catfish) %>% as.numeric()*0.8, 
                             Site == "Sister3" ~ st_area(sister3) %>% as.numeric()*1.25, 
                             Site == "Pick" ~ st_area(pick) %>% as.numeric()*1.58), 
         res_time_day = (Vol_m3/q)* (1/86400))

st_area(deans) %>% as.numeric() *1e-6
st_area(catfish) %>% as.numeric() *1e-6
st_area(sister3) %>% as.numeric() *1e-6
st_area(pick) %>% as.numeric() *1e-6


```

We sampled 4 sites over at least one 24 hr period. We installed 25 ebullition traps across 5 transects in each impoundment. Every 3 hours, we recorded the volume of gas accumulated in each ebullition trap and took a diffusive flux measurement immediately adjacent to 10 if the ebullition traps across the impoundment. To determine impoundment area, I digitized the impoundments using high resolution (0.5 ft) orthoimagery captured during the leaf off period. Pick has a beaver dam on the inlet stream and I delineated only to the beaver dam.

```{r render map, echo = F}
mapview(deans, col.regions = "#DCE319FF", alpha.regions = 1)+
  mapview(catfish, col.regions = "#55C667FF", alpha.regions = 1)+
  mapview(sister3, col.regions = "#440154FF", alpha.regions = 1)+
  mapview(pick, col.regions = "#2D708EFF", alpha.regions = 1)+
  mapview(trap_locations, col.regions = "grey", alpha.regions = 1, legend = F)+
  mapview(inlet_locations, col.regions = "black", alpha.regions = 1)
```


|Site      |Area (km^2^)|Max Depth (m)|Mean Depth (m)|Residence Time|Dates Sampled  |
|----------|------------|-------------|--------------|--------------|---------------|
|Deans     |0.0041      |3.52         |2.03          |              |8/16/22 - 8/17/22<br />8/30/22 - 8/31/22|
|Sister 3  |0.0012      |2.27         |1.25          |              |8/22/22 - 8/23/22|
|Catfish   |0.0018      |1.98         |0.80          |              |9/6/22 - 9/7/22<br />9/18/22 - 9/19/22|
|Pick      |0.0077      |3.80         |1.58          |              |8/22/22 - 8/23/22|


## Dissolved oxygen 

We recorded dissolved oxygen every 15 minutes 0.25 m below the surface in every impoundment. From 6/20/22 to 7/13/22, we also recorded dissolved oxygen 0.1m from the bottom of Pick in the deepest location in the impoundment. Because dissolved oxygen was consistently 0 mg/L, we reallocated our oxygen sensors and installed both a top and bottom DO sensor in Sister 3. 

```{r read do data, include = F}
do_list <- list.files("2-Clean Data/do")

for(i in 1:length(do_list)){
  temporary <- fread(paste0("2-Clean Data/do/", do_list[i])) %>% 
  slice(-1) %>% 
  mutate(DO_mgL = as.numeric(DO_mgL), Date_Time = ymd_hms(Date_Time, tz="America/New_York"))
  
  assign(str_extract(do_list[i], ".*(?=\\.)"), 
         as.xts(temporary$DO_mgL, order.by = temporary$Date_Time)
         )
}
```

### Deans
```{r Deans DO plot, echo = F}
dygraph(Deans_DO_Top) %>% 
  dyOptions(colors = "#DCE319FF") %>% 
  dyAxis("y", label = "Dissolved Oxygen (mg/L)")
```

### Catfish
```{r Catfish DO plot, echo = F}
dygraph(Catfish_DO_Top) %>% 
  dyOptions(colors = "#55C667FF")%>% 
  dyAxis("y", label = "Dissolved Oxygen (mg/L)")
```

### Sister 3
```{r Sister DO plot, echo = F}
Sister_DO <- cbind(Sister_DO_Top, Sister_DO_Bottom)

pal <- c("#440154FF", "#AF97B5")
dygraph(Sister_DO) %>% 
  dyOptions(colors = pal)%>% 
  dyAxis("y", label = "Dissolved Oxygen (mg/L)")
```

### Pick
```{r Pick DO plot, echo = F}
Pick_DO <- cbind(Pick_DO_Top, Pick_DO_Bottom)

pal <- c("#2D708EFF","#a3cdff")
dygraph(Pick_DO) %>% 
  dyOptions(colors = pal)%>% 
  dyAxis("y", label = "Dissolved Oxygen (mg/L)")
```

### All impoundments top DO
```{r all do, echo = F}
pal <- c("#DCE319FF",  "#55C667FF", "#440154FF", "#2D708EFF")

all_DO <- cbind(Deans_DO_Top, Catfish_DO_Top, Sister_DO_Top, Pick_DO_Top)
dygraph(all_DO) %>% 
   dyOptions(colors = pal)%>% 
  dyAxis("y", label = "Dissolved Oxygen (mg/L)")
```

## Temperature

```{r read temperature data, echo = F}
temp_list <- list.files("2-Clean Data/temperature")

for(i in 1:length(temp_list)){
  temporary <- read.csv(paste0("2-Clean Data/temperature/", temp_list[i])) %>% 
  mutate(temp = as.numeric(temp), date = ymd_hms(date, tz="America/New_York"))
  
  assign(str_extract(temp_list[i], ".*(?=\\.)"), 
         temporary %>% filter(is.na(temp)==F)
         )
}
```


### Deans
```{r Deans temp, echo = F}
deans_vec <- temp_list %>% str_subset("deans") %>% str_extract(".*(?=\\.)")

deans_date <- NULL
for(i in 1:length(deans_vec)){
  deans_date <- deans_date %>% bind_rows(eval(sym(deans_vec[i])) %>% select(date))
}
deans_date <- tibble(distinct(deans_date))
  
for(i in 1:length(deans_vec)){
  temporary <- eval(sym(deans_vec[i])) %>% 
    full_join(deans_date, by = "date")  %>% arrange(date) %>% na.locf()
  
  assign(paste0(deans_vec[i], "_xts"), as.xts(temporary$temp, order.by = temporary$date))
}


deans_temp <- cbind(deans_0.25_xts, deans_0.75_xts, deans_1.25_xts, deans_2.75_xts)
dygraph(deans_temp) %>% 
  dyOptions(connectSeparatedPoints = TRUE) %>% 
  dyAxis("y", label = "Temperature (C)")
```

### Catfish
```{r Catfish temp, echo = F}
catfish_vec <- temp_list %>% str_subset("catfish") %>% str_extract(".*(?=\\.)")

catfish_date <- NULL
for(i in 1:length(catfish_vec)){
  catfish_date <- catfish_date %>% bind_rows(eval(sym(catfish_vec[i])) %>% select(date))
}
catfish_date <- tibble(distinct(catfish_date))
  
for(i in 1:length(catfish_vec)){
  temporary <- eval(sym(catfish_vec[i])) %>% 
    full_join(catfish_date, by = "date")  %>% arrange(date) %>% na.locf()
  
  assign(paste0(catfish_vec[i], "_xts"), as.xts(temporary$temp, order.by = temporary$date))
}

# something weird is happening in the middle of the time series
catfish_temp <- cbind(catfish_0.25_xts, catfish_1.25_xts, catfish_1.75_xts)
dygraph(catfish_temp) %>% 
  dyOptions(connectSeparatedPoints = TRUE)%>% 
  dyAxis("y", label = "Temperature (C)")
```

### Sister 3
```{r Sister3 temp, echo = F}
sister_vec <- temp_list %>% str_subset("sister") %>% str_extract(".*(?=\\.)")

sister_date <- NULL
for(i in 1:length(sister_vec)){
  sister_date <- sister_date %>% bind_rows(eval(sym(sister_vec[i])) %>% select(date))
}
sister_date <- tibble(distinct(sister_date))
  
for(i in 1:length(sister_vec)){
  temporary <- eval(sym(sister_vec[i])) %>% 
    full_join(sister_date, by = "date")  %>% arrange(date) %>% na.locf()
  
  assign(paste0(sister_vec[i], "_xts"), as.xts(temporary$temp, order.by = temporary$date))
}

# something weird is happening in the middle of the time series
sister_temp <- cbind(sister_0.25_xts, sister_0.75_xts, sister_1.50_xts, sister_2.00_xts)
dygraph(sister_temp) %>% 
  dyOptions(connectSeparatedPoints = TRUE)%>% 
  dyAxis("y", label = "Temperature (C)")
```

### Pick
```{r Pick temp, echo = F}
pick_vec <- temp_list %>% str_subset("pick") %>% str_extract(".*(?=\\.)")

pick_date <- NULL
for(i in 1:length(pick_vec)){
  pick_date <- pick_date %>% bind_rows(eval(sym(pick_vec[i])) %>% select(date))
}
pick_date <- tibble(distinct(pick_date))
  
for(i in 1:length(pick_vec)){
  temporary <- eval(sym(pick_vec[i])) %>% 
    full_join(pick_date, by = "date")  %>% arrange(date) %>% na.locf() %>% filter(date < ymd_hms("2022-11-09 10:00:00", tz = "America/New_York")) %>% filter(!(date > ymd_hms("2022-07-07 10:16:00", tz = "America/New_York") & date < ymd_hms("2022-07-07 11:16:00", tz = "America/New_York")))
  
  if(temporary$depth[1]==3){
    temporary <- temporary %>% filter(date < ymd_hms("2022-07-07 10:15:00", tz = "America/New_York"))
  }
  
  assign(paste0(pick_vec[i], "_xts"), as.xts(temporary$temp, order.by = temporary$date))
}

pick_temp <- cbind(pick_0.25_xts, pick_0.75_xts, pick_1.75_xts, pick_2.25_xts, pick_3.00_xts)
dygraph(pick_temp) %>% 
  dyOptions(connectSeparatedPoints = TRUE)%>% 
  dyAxis("y", label = "Temperature (C)")
```

