--- 
title: "Naslund Chapter 1 Analysis"
author: "Laura Naslund"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography:
- book.bib
- packages.bib
description: |
  This is the documentation of an analysis of spatial and temporal variability of greenhouse gas emissions from small reservoirs
link-citations: yes
github-repo: "rstudio/bookdown-demo"
---

# Sampling scheme

```{r load packages, include=F}
my_packages <- c("tidyverse", "mapview", "lubridate", "sf", "data.table", "dygraphs", "xts", "gstat", "stars", "automap", "viridis", "tmap", "gridExtra", "lme4", "AICcmodavg", "ggeffects", "lmerTest", "plotly", "performance", "hms", "cowplot", "MuMIn", "glmmTMB")
lapply(my_packages, require, character.only = TRUE)

source("data_munge_functions.R")

options(dplyr.summarise.inform = FALSE)
```

```{r load dfs, include = F}
# Trap locations and pond polygons in WGS 84 / UTM zone 17N

# Create sf object of ebullition trap locations
trap_locations <- read.csv("2-Clean Data/ebullition-trap-locations.csv") %>% 
  filter(str_sub(Name, 2,2) %>% str_detect("[:alpha:]")==F) %>% 
  st_as_sf(coords = c("Longitude", "Latitude"), crs=4326) %>% 
  st_transform(crs = 32617)%>% 
  mutate(Site = case_when(
    str_sub(Name, 1, 1) == "P" ~"Pick",
    str_sub(Name, 1, 1) == "D" ~"Deans",
    str_sub(Name, 1, 1) == "S" ~"Sister3",
    str_sub(Name, 1, 1) == "C" ~"Catfish",
  )) %>% 
  select(-Description)

# Create sf object of pond inlets
inlet_locations <- read.csv("2-Clean Data/inlet-locations.csv") %>% 
  st_as_sf(coords = c("Longitude", "Latitude"), crs=4326) %>% 
  st_transform(crs = 32617)

# Create sf objects of ponds
deans <- read_sf("2-Clean Data/site_shapefiles/Deans.shp") %>% 
  st_transform(crs = 32617)
catfish <- read_sf("2-Clean Data/site_shapefiles/Catfish.shp") %>% 
  st_transform(crs = 32617)
sister3 <- read_sf("2-Clean Data/Site_Shapefiles/Sister3.shp") %>% 
  st_transform(crs = 32617)
pick <- read_sf("2-Clean Data/Site_Shapefiles/Pick.shp") %>% # in published work called Blue Herron
  st_transform(crs = 32617)
```


We sampled 4 sites over at least one 24 hr period. We installed 25 ebullition traps across 5 transects in each impoundment. Every 3 hours, we recorded the volume of gas accumulated in each ebullition trap and took a diffusive flux measurement immediately adjacent to 10 if the ebullition traps across the impoundment. To determine impoundment area, I digitized the impoundments using high resolution (0.5 ft) orthoimagery captured during the leaf off period. Pick has a beaver dam on the inlet stream and I delineated only to the beaver dam.

```{r render map, echo = F}
mapviewOptions(basemaps = c("CartoDB.Positron"))
mapview(deans, col.regions = "#DCE319FF", alpha.regions = 1)+
  mapview(catfish, col.regions = "#55C667FF", alpha.regions = 1)+
  mapview(sister3, col.regions = "#440154FF", alpha.regions = 1)+
  mapview(pick, col.regions = "#2D708EFF", alpha.regions = 1)+
  mapview(trap_locations, col.regions = "grey", alpha.regions = 1, legend = F)+
  mapview(inlet_locations, col.regions = "black", alpha.regions = 1)
```

```{r site map, include = F}
mapshot(
 mapview(deans, col.regions = "#2D708EFF", alpha.regions = 1, legend = FALSE, homebutton=FALSE)+
  mapview(catfish, col.regions = "#2D708EFF", alpha.regions = 1, legend = FALSE, homebutton=FALSE)+
  mapview(sister3, col.regions = "#2D708EFF", alpha.regions = 1, legend = FALSE, homebutton=FALSE)+
  mapview(pick, col.regions = "#2D708EFF", alpha.regions = 1, legend = FALSE, homebutton=FALSE),
  file = "site_map.png",
 remove_controls = c("zoomControl", "layersControl", "homeButton", 
    "drawToolbar", "easyButton"),
)
```


|Site      |Area (km^2^)|Max Depth (m)|Mean Depth (m)|Residence Time (days)|Dates Sampled  |
|----------|------------|-------------|--------------|---------------------|---------------|
|Deans     |0.0041      |3.52         |2.03          |         46          |8/16/22 - 8/17/22<br />8/30/22 - 8/31/22|
|Sister 3  |0.0012      |2.27         |1.25          |         20          |8/22/22 - 8/23/22|
|Catfish   |0.0018      |1.98         |0.80          |         19          |9/06/22 - 9/07/22<br />9/18/22 - 9/19/22|
|Pick      |0.0077      |3.80         |1.58          |         45          |8/22/22 - 8/23/22|


## Dissolved oxygen 

We recorded dissolved oxygen every 15 minutes 0.25 m below the surface in every impoundment. From 6/20/22 to 7/13/22, we also recorded dissolved oxygen 0.1m from the bottom of Pick in the deepest location in the impoundment. Because dissolved oxygen was consistently 0 mg/L, we reallocated our oxygen sensors and installed both a top and bottom DO sensor in Sister 3. 

```{r read do data, include = F}
do_list <- list.files("2-Clean Data/do")
do <- NULL

for(i in 1:length(do_list)){
  temporary <- fread(paste0("2-Clean Data/do/", do_list[i])) %>% 
  slice(-1) %>% 
  mutate(DO_mgL = as.numeric(DO_mgL), Date_Time = ymd_hms(Date_Time, tz="America/New_York"), site = str_extract(do_list[i], "[:alpha:]+(?=_)"), location = str_extract(do_list[i], "(?<=_)[:alpha:]+(?=\\.)"))
  
   do <- bind_rows(do, temporary)
  
  assign(str_extract(do_list[i], ".*(?=\\.)"), 
         as.xts(temporary$DO_mgL, order.by = temporary$Date_Time)
         )
}

do <- sampling_filter_24hr(do %>%
  mutate(site = if_else(site == "Pick", "Blue Herron", site)))
```

### Deans
```{r Deans DO plot, echo = F}
dygraph(Deans_DO_Top) %>% 
  dyOptions(colors = "#DCE319FF") %>% 
  dyAxis("y", label = "Dissolved Oxygen (mg/L)")
```

### Catfish
```{r Catfish DO plot, echo = F}
dygraph(Catfish_DO_Top) %>% 
  dyOptions(colors = "#55C667FF")%>% 
  dyAxis("y", label = "Dissolved Oxygen (mg/L)")
```

### Sister
```{r Sister DO plot, echo = F}
Sister_DO <- cbind(Sister_DO_Top, Sister_DO_Bottom)

pal <- c("#440154FF", "#AF97B5")
dygraph(Sister_DO) %>% 
  dyOptions(colors = pal)%>% 
  dyAxis("y", label = "Dissolved Oxygen (mg/L)")
```

### Blue Herron
```{r Pick DO plot, echo = F}
Pick_DO <- cbind(Pick_DO_Top, Pick_DO_Bottom)

pal <- c("#2D708EFF","#a3cdff")
dygraph(Pick_DO) %>% 
  dyOptions(colors = pal)%>% 
  dyAxis("y", label = "Dissolved Oxygen (mg/L)")
```

### All impoundments top DO
```{r all do, echo = F}
pal <- c("#DCE319FF",  "#55C667FF", "#440154FF", "#2D708EFF")

all_DO <- cbind(Deans_DO_Top, Catfish_DO_Top, Sister_DO_Top, Pick_DO_Top)
dygraph(all_DO) %>% 
   dyOptions(colors = pal)%>% 
  dyAxis("y", label = "Dissolved Oxygen (mg/L)")
```

```{r do time series, echo = F}
anno <- data.frame(
  x1 = c(ymd_hms("2022-09-06 08:00:00", tz = "America/New_York"), 
         ymd_hms("2022-09-18 08:00:00", tz = "America/New_York"), 
         ymd_hms("2022-08-16 08:00:00", tz = "America/New_York"), 
         ymd_hms("2022-08-30 08:00:00", tz = "America/New_York"), 
         ymd_hms("2022-09-13 08:00:00", tz = "America/New_York"), 
         ymd_hms("2022-08-22 08:00:00", tz = "America/New_York") ),
  x2 = c(ymd_hms("2022-09-07 08:00:00", tz = "America/New_York"), 
         ymd_hms("2022-09-19 08:00:00", tz = "America/New_York"), 
         ymd_hms("2022-08-17 08:00:00", tz = "America/New_York"), 
         ymd_hms("2022-08-31 08:00:00", tz = "America/New_York"), 
         ymd_hms("2022-09-14 08:00:00", tz = "America/New_York"), 
         ymd_hms("2022-08-23 08:00:00", tz = "America/New_York")),
  y1 = c(rep(0,6)),
  y2 = c(rep(11,6)),
  site = c("Catfish", "Catfish", "Deans", "Deans", "Blue Herron", "Sister"))

do_crop <- do %>% filter(location == "Top") %>% 
  filter(Date_Time > ymd_hms("2022-08-01 08:00:00"), Date_Time < ymd_hms("2022-09-30 08:00:00"))

png(filename = "4-Figures/do-all-summary.png", width = 8, height = 7, units = "in", res = 300)
ggplot() +
   geom_rect(data = anno, aes(xmin = x1, xmax = x2, ymin = y1, ymax = y2), fill = "#a3cdff", alpha = 0.5)+
  geom_line(data = do_crop, aes(Date_Time, DO_mgL))+
  theme_bw()+
  ylab("DO (mg/L)") + 
  theme(axis.title.x = element_blank(), axis.text = element_text(size = 14, color = "black"), 
        axis.title = element_text(size = 16, color = "black"), strip.text = element_text(size = 14,  color = "black"))+
  facet_grid(rows = vars(site))
dev.off()
```

```{r do during sampling, echo = F}
time_vec <- c("10:00", "13:00", "16:00", "19:00", "22:00", "01:00", "04:00", "07:00")
date_time_vec_1 <- do.call(c, map(time_vec[1:5], function(x) ymd_hm(paste(date(Sys.time()), x, sep = " "), tz = "America/New_York")))
date_time_vec_2 <- do.call(c, map(time_vec[6:8], function(x) ymd_hm(paste(date(Sys.time()+days(1)), x, sep = " "), tz = "America/New_York")))
date_time_vec <- c(date_time_vec_1, date_time_vec_2)

png(filename = "4-Figures/do-sampling-summary.png", width = 8, height = 5, units = "in", res = 300)
daily_trace_aes(do %>% filter(location == "Top") %>% mutate(site = if_else(site == "Pick", "Blue Herron", site)) %>% 
  filter(is.na(sampling)==F) %>% 
     mutate(time = format(Date_Time, format = "%H:%M") %>% as.POSIXct(format = "%H:%M"), time_alt = if_else(hour(time) %in% c(24, 0:9), time + days(1), time)) %>% 
  ggplot(aes(time_alt, DO_mgL, group = sampling)) +
  geom_line()+
  ylab("DO (mg/L)"), date_time_vec)
dev.off()
```

Summary of DO during sampling
```{r summary sampling do, echo = F}
do %>% filter(location == "Top") %>% 
  mutate(site = if_else(site == "Pick", "Blue Herron", site)) %>% 
  filter(is.na(sampling)==F) %>% 
  group_by(site) %>% 
  summarize(min_do = min(DO_mgL), max_do = max(DO_mgL), mean_do = mean(DO_mgL))
```

## Temperature
```{r read temperature data, echo = F}
temp_list <- list.files("2-Clean Data/temperature")
all_temps <- NULL

for(i in 1:length(temp_list)){
  temporary <- read.csv(paste0("2-Clean Data/temperature/", temp_list[i])) %>% 
  mutate(temp = as.numeric(temp), date = ymd_hms(date, tz="America/New_York"))
  all_temps <- bind_rows(all_temps, temporary)
  
  assign(str_extract(temp_list[i], ".*(?=\\.)"), 
         temporary %>% filter(is.na(temp)==F)
         )
}

all_temps <- sampling_filter_24hr(all_temps %>% mutate(Date_Time = date) %>% 
    mutate(site = if_else(site == "Pick", "Blue Herron", if_else(site == "Sister3", "Sister", site)))) %>% 
  select(-Date_Time)

png(filename = "4-Figures/daily-temp.png", width = 8, height = 5, units = "in", res = 300)
daily_trace_aes(ggplot(all_temps %>% filter(is.na(sampling) == F, depth == 0.25) %>% mutate(time = format(date, format = "%H:%M") %>% as.POSIXct(format = "%H:%M"), time_alt = if_else(hour(time) %in% c(24, 0:9), time + days(1), time)), aes(time_alt, temp, group = sampling)) + 
  geom_line() + ylab("Temperature (°C)"), date_time_vec)
dev.off()

top_temp <- sampling_filter_28hr(all_temps %>% 
  filter(is.na(sampling)==F, depth == 0.25))
```

You are here for cleaning
### Deans
```{r Deans temp, echo = F}
deans_vec <- temp_list %>% str_subset("deans") %>% str_extract(".*(?=\\.)")

deans_date <- NULL
for(i in 1:length(deans_vec)){
  deans_date <- deans_date %>% bind_rows(eval(sym(deans_vec[i])) %>% select(date))
}
deans_date <- tibble(distinct(deans_date))
  
for(i in 1:length(deans_vec)){
  temporary <- eval(sym(deans_vec[i])) %>% 
    full_join(deans_date, by = "date")  %>% arrange(date) %>% na.locf()
  
  assign(paste0(deans_vec[i], "_xts"), as.xts(temporary$temp, order.by = temporary$date))
}

deans_temp <- cbind(deans_0.25_xts, deans_0.75_xts, deans_1.25_xts, deans_2.75_xts)
dygraph(deans_temp) %>% 
  dyOptions(connectSeparatedPoints = TRUE) %>% 
  dyAxis("y", label = "Temperature (C)")
```

### Catfish
```{r Catfish temp, echo = F}
catfish_vec <- temp_list %>% str_subset("catfish") %>% str_extract(".*(?=\\.)")

catfish_date <- NULL
for(i in 1:length(catfish_vec)){
  catfish_date <- catfish_date %>% bind_rows(eval(sym(catfish_vec[i])) %>% select(date))
}
catfish_date <- tibble(distinct(catfish_date))
  
for(i in 1:length(catfish_vec)){
  temporary <- eval(sym(catfish_vec[i])) %>% 
    full_join(catfish_date, by = "date")  %>% arrange(date) %>% na.locf()
  
  assign(paste0(catfish_vec[i], "_xts"), as.xts(temporary$temp, order.by = temporary$date))
}

# something weird is happening in the middle of the time series
catfish_temp <- cbind(catfish_0.25_xts, catfish_1.25_xts, catfish_1.75_xts)
dygraph(catfish_temp) %>% 
  dyOptions(connectSeparatedPoints = TRUE)%>% 
  dyAxis("y", label = "Temperature (C)")
```

### Sister 3
```{r Sister3 temp, echo = F}
sister_vec <- temp_list %>% str_subset("sister") %>% str_extract(".*(?=\\.)")

sister_date <- NULL
for(i in 1:length(sister_vec)){
  sister_date <- sister_date %>% bind_rows(eval(sym(sister_vec[i])) %>% select(date))
}
sister_date <- tibble(distinct(sister_date))
  
for(i in 1:length(sister_vec)){
  temporary <- eval(sym(sister_vec[i])) %>% 
    full_join(sister_date, by = "date")  %>% arrange(date) %>% na.locf()
  
  assign(paste0(sister_vec[i], "_xts"), as.xts(temporary$temp, order.by = temporary$date))
}

# something weird is happening in the middle of the time series
sister_temp <- cbind(sister_0.25_xts, sister_0.75_xts, sister_1.50_xts, sister_2.00_xts)
dygraph(sister_temp) %>% 
  dyOptions(connectSeparatedPoints = TRUE)%>% 
  dyAxis("y", label = "Temperature (C)")
```

### Blue Herron
```{r Pick temp, echo = F}
pick_vec <- temp_list %>% str_subset("pick") %>% str_extract(".*(?=\\.)")

pick_date <- NULL
for(i in 1:length(pick_vec)){
  pick_date <- pick_date %>% bind_rows(eval(sym(pick_vec[i])) %>% select(date))
}
pick_date <- tibble(distinct(pick_date))
  
for(i in 1:length(pick_vec)){
  temporary <- eval(sym(pick_vec[i])) %>% 
    full_join(pick_date, by = "date")  %>% arrange(date) %>% na.locf() %>% filter(date < ymd_hms("2022-11-09 10:00:00", tz = "America/New_York")) %>% filter(!(date > ymd_hms("2022-07-07 10:16:00", tz = "America/New_York") & date < ymd_hms("2022-07-07 11:16:00", tz = "America/New_York")))
  
  if(temporary$depth[1]==3){
    temporary <- temporary %>% filter(date < ymd_hms("2022-07-07 10:15:00", tz = "America/New_York"))
  }
  
  assign(paste0(pick_vec[i], "_xts"), as.xts(temporary$temp, order.by = temporary$date))
}

pick_temp <- cbind(pick_0.25_xts, pick_0.75_xts, pick_1.75_xts, pick_2.25_xts, pick_3.00_xts)
dygraph(pick_temp) %>% 
  dyOptions(connectSeparatedPoints = TRUE)%>% 
  dyAxis("y", label = "Temperature (C)")
```

## PAR
All sensors were submerged ~0.25m below the water surface
```{r par set up, include = F}
# need to confirm calibrated units, probably umol/m2/s
par <- read.csv("2-Clean Data/par-data.csv") %>% mutate(date_time = ymd_hms(date_time, tz = "America/New_York"))

deans.xts <- as.xts(par %>% filter(site == "Deans", date_time < ymd_hms("2022-08-17 09:50:00")) %>% pull(calibrated), order.by = par %>% filter(site == "Deans", date_time < ymd_hms("2022-08-17 09:50:00")) %>% pull(date_time))
catfish.xts <- as.xts(par %>% filter(site == "Catfish") %>% pull(calibrated), order.by = par %>% filter(site == "Catfish") %>% pull(date_time))
pick.xts <- as.xts(par %>% filter(site == "Pick", is.na(date_time)==FALSE) %>% pull(calibrated), order.by = par %>% filter(site == "Pick", is.na(date_time)==FALSE) %>% pull(date_time))
sister3.xts <- as.xts(par %>% filter(site == "Sister3", is.na(date_time)==FALSE) %>% pull(calibrated), order.by = par %>% filter(site == "Sister3", is.na(date_time)==FALSE) %>% pull(date_time))
```

### Deans
Sensor casing cracked, so no available PAR data for second Deans sampling
```{r deans par, echo = F}
dygraph(deans.xts) %>% 
  dyOptions(colors = "#DCE319FF") %>% 
  dyAxis("y", label = "PAR (umol/m2/s)")
```

8/16/22
```{r deans day par, echo = F}
deans16.xts <- as.xts(par %>% filter(site == "Deans", date_time > ymd_hms("2022-08-16 06:00:00", tz = "America/New_York"), date_time < ymd_hms("2022-08-17 09:50:00", tz = "America/New_York")) %>% pull(calibrated), order.by = par %>% filter(site == "Deans", date_time > ymd_hms("2022-08-16 06:00:00", tz = "America/New_York"), date_time < ymd_hms("2022-08-17 09:50:00", tz = "America/New_York")) %>% pull(date_time))

dygraph(deans16.xts) %>% 
  dyOptions(colors = "#DCE319FF") %>% 
  dyAxis("y", label = "PAR (umol/m2/s)")
```

### Catfish
```{r catfish par, echo = F}
dygraph(catfish.xts) %>% 
  dyOptions(colors = "#55C667FF") %>% 
  dyAxis("y", label = "PAR (umol/m2/s)")
```

9/6/22
```{r catfish day par, echo = F}
catfish06_same.xts <-
  as.xts(
    par %>% filter(
      site == "Catfish",
      date_time > ymd_hms("2022-09-06 06:00:00", tz = "America/New_York"),
      date_time < ymd_hms("2022-09-07 12:00:00", tz = "America/New_York")
    ) %>% mutate(
      date_time_same = if_else(date == "06/09/2022 ", paste0("1900-01-01", time) %>% ymd_hms(tz = "America/New_York"), paste0("1900-01-02", time) %>% ymd_hms(tz = "America/New_York"))
    ) %>% pull(calibrated),
    order.by = par %>% filter(
      site == "Catfish",
      date_time > ymd_hms("2022-09-06 06:00:00", tz = "America/New_York"),
      date_time < ymd_hms("2022-09-07 12:00:00", tz = "America/New_York")
    ) %>% mutate(
      date_time_same = if_else(date == "06/09/2022 ", paste0("1900-01-01", time) %>% ymd_hms(tz = "America/New_York"), paste0("1900-01-02", time) %>% ymd_hms(tz = "America/New_York"))
    ) %>% pull(date_time_same)
  )

dygraph(catfish06_same.xts)

catfish18_same.xts <-
  as.xts(
    par %>% filter(
      site == "Catfish",
      date_time > ymd_hms("2022-09-18 06:00:00", tz = "America/New_York"),
      date_time < ymd_hms("2022-09-19 12:00:00", tz = "America/New_York")
    ) %>% mutate(
      date_time_same = if_else(date == "18/09/2022 ", paste0("1900-01-01", time) %>% ymd_hms(tz = "America/New_York"), paste0("1900-01-02", time) %>% ymd_hms(tz = "America/New_York"))
    ) %>% pull(calibrated),
    order.by = par %>% filter(
      site == "Catfish",
      date_time > ymd_hms("2022-09-18 06:00:00", tz = "America/New_York"),
      date_time < ymd_hms("2022-09-19 12:00:00", tz = "America/New_York")
    ) %>% mutate(
      date_time_same = if_else(date == "18/09/2022 ", paste0("1900-01-01", time) %>% ymd_hms(tz = "America/New_York"), paste0("1900-01-02", time) %>% ymd_hms(tz = "America/New_York"))
    ) %>% pull(date_time_same)
  )

catfish_day.xts <- cbind(catfish06_same.xts, catfish18_same.xts)

pal <- c("#55C667FF", "#143C1B")
dygraph(catfish_day.xts) %>% 
  dyOptions(colors = pal) %>% 
  dyAxis("y", label = "PAR (umol/m2/s)")
```

### Pick
```{r pick par, echo = F}
dygraph(pick.xts) %>% 
  dyOptions(colors = "#440154FF") %>% 
  dyAxis("y", label = "PAR (umol/m2/s)")
```

#9/13/22
```{r pick day par, echo = F}
pick13.xts <- as.xts(par %>% filter(site == "Pick", date_time > ymd_hms("2022-09-13 06:00:00", tz = "America/New_York"), date_time < ymd_hms("2022-09-14 12:00:00", tz = "America/New_York")) %>% pull(calibrated), order.by = par %>% filter(site == "Pick", date_time > ymd_hms("2022-09-13 06:00:00", tz = "America/New_York"), date_time < ymd_hms("2022-09-14 12:00:00", tz = "America/New_York")) %>% pull(date_time))

dygraph(pick13.xts) %>% 
  dyOptions(colors = "#440154FF") %>% 
  dyAxis("y", label = "PAR (umol/m2/s)")
```

### Sister3
```{r sister3 par, echo = F}
dygraph(sister3.xts) %>% 
  dyOptions(colors = "#2D708EFF") %>% 
  dyAxis("y", label = "PAR (umol/m2/s)")
```

#8/22/22
```{r sister3 day par, echo = F}
sister322.xts <- as.xts(par %>% filter(site == "Sister3", date_time > ymd_hms("2022-08-22 06:00:00", tz = "America/New_York"), date_time < ymd_hms("2022-08-23 12:00:00", tz = "America/New_York")) %>% pull(calibrated), order.by = par %>% filter(site == "Sister3", date_time > ymd_hms("2022-08-22 06:00:00", tz = "America/New_York"), date_time < ymd_hms("2022-08-23 12:00:00", tz = "America/New_York")) %>% pull(date_time))

dygraph(sister322.xts) %>% 
  dyOptions(colors = "#2D708EFF") %>% 
  dyAxis("y", label = "PAR (umol/m2/s)")
```

## Dissolved gas concentrations
I sampled for dissolved gas 0.25 m from the surface of the impoundments, 0.1m from the bottom, in the inlet stream, and in the outlet stream. The dissolved gas samples from Catfish on 9/18/22-9/19/22 were not handled properly, thus those values are excluded from the summaries.
```{r dissolved gas conc, echo = F}
gc <- read.csv("2-Clean Data/dissolved-gas.csv")

gc_summarized <- gc %>% mutate_if(is.character, 
                str_replace_all, 
                pattern = "Picks", 
                replacement = "Pick") %>% 
  mutate_if(is.character, 
                str_replace_all, 
                pattern = "oulet", 
                replacement = "outlet")%>% 
  group_by(Site, Collection.Date, Location) %>% 
  summarize(CH4_avg_umol = mean(Original_Liq_CH4_umol), CO2_avg_umol = mean(Original_Liq_CO2_umol), CH4_sd = sd(Original_Liq_CH4_umol, na.rm = T), CO2_sd = sd(Original_Liq_CO2_umol, na.rm = T), reps = n()) %>% # umol/L
  mutate(Location = factor(Location, levels = c("top","bottom", "inlet", "outlet")))

gc_summarized %>% filter(mdy(Collection.Date)>mdy("08/15/22"), Collection.Date!="9/19/2022") %>% arrange(Location, desc(CH4_avg_umol)) %>% select(Site, Collection.Date, Location, CH4_avg_umol, CH4_sd, CO2_avg_umol, CO2_sd) 
```

## Wind Speed
We took two 15 second averaged windspeed measurements over the course of each diffusive flux measurement. Note different x-axis scales. 
```{r wind speed, echo = F}
#png(filename = "4-Figures/wind-speed.png", width = 9, height = 5, units = "in", res = 300)
ws <- read.csv("2-Clean Data/anemom_all.csv") %>% mutate(Trip == as.factor(Trip)) %>% 
  mutate(sampling = case_when(sampling == "Catfish1" ~"Catfish 9/06/22",
                              sampling == "Catfish2" ~ "Catfish 9/18/22",
                              sampling == "Deans1" ~ "Deans 8/16/22",
                              sampling == "Deans2" ~ "Deans 8/30/22", 
                              sampling == "Pick1" ~ "Pick 9/13/22",
                              sampling == "Sister31" ~ "Sister3 8/22/22"))


ggplot(ws, aes(as.factor(Trip), ws_avg))+
  geom_boxplot() + 
  facet_wrap(~sampling, scales = "free")+
  scale_x_discrete(breaks = c("1", "2", "3", "4", "5", "6", "7", "8"),
    labels = c("10AM", "1PM", "4PM", "7PM", "10PM", "1AM", "4AM", "7AM"))+
  ylab("Wind Speed (m/s)") + 
  theme_bw()+
  theme(axis.title.x = element_blank(), 
        axis.text = element_text(size=14, color = "black"), 
        axis.text.x = element_text(angle = 45, hjust = 1), 
        axis.title.y = element_text(size=16, color = "black"), 
        strip.text = element_text(size=14, color = "black"))
#dev.off()

```


## Residence time calculation 
I took a point estimate of discharge from the ponds while sampling, but these discharge values gave unrealistic residence times. I instead calculated discharge from a regional regression equation using average annual precipitation and watershed area (Gotvald et al. 2017). 

```{r res time calc, include = F}
# discharge estimates from measurements seem unrealistic. It probably makes more sense to use a regional relationship between watershed area and discharge. 

# need to assign outlet point, delineate the watershed and then calculate MAP from Gotvald report regression relationship 

q <- read.csv("2-Clean Data/discharge.csv") %>% 
  mutate(q = ((Vol_ml*10^-6)/Time_s), 
         Vol_m3 = case_when(Site == "Deans" ~ st_area(deans) %>% as.numeric()*2.03, 
                             Site == "Catfish" ~ st_area(catfish) %>% as.numeric()*0.8, 
                             Site == "Sister3" ~ st_area(sister3) %>% as.numeric()*1.25, 
                             Site == "Pick" ~ st_area(pick) %>% as.numeric()*1.58), 
         res_time_day = (Vol_m3/q)* (1/86400))

st_area(deans) %>% as.numeric() *1e-6
st_area(catfish) %>% as.numeric() *1e-6
st_area(sister3) %>% as.numeric() *1e-6
st_area(pick) %>% as.numeric() *1e-6

# https://pubs.er.usgs.gov/publication/sir20175001

# (9.20 × 10–6)(DRNAREA)0.993(PRECIP)2.97
# Drainage area is in square miles, precip
# 48.7 inches from PRISM

# Pick ws area 301000 m2
# Sister3 ws area 79700 m2
# Catfish ws area 80600 m2
# Deans ws area 202600 m2

res_time <- data.frame(
  site = c("Pick", "Sister3", "Catfish", "Deans"),
  ws_area_m2 = c(301000, 79700, 80600, 202600), 
  pond_vol_m3 = c(st_area(pick) %>% as.numeric()*1.58, st_area(sister3) %>% as.numeric()*1.25, st_area(catfish) %>% as.numeric()*0.8, st_area(deans) %>% as.numeric()*2.03)
) %>% 
  mutate(ws_area_sqmil = ws_area_m2 * 3.86102e-7, 
         qa_ft3s = (9.2 * 10^-6)*((ws_area_sqmil)^0.993)*((48.7)^2.97), 
         qa_m3s = qa_ft3s * 0.0283168, 
         res_time_s = pond_vol_m3/qa_m3s, 
         res_time_d = res_time_s *(1/86400))
```

```{r}
to_remove <- ls()[!ls() %in% c("catfish", "deans", "pick", "sister3", "trap_locations", "inlet_locations", "top_temp")]

rm(list = to_remove)
```

